---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# amoter

The goal of amoter is to provde a collection of tools that make it easy to 
analyse (animal) movement in relation terrain shape.

## Example

Consider the case where you would like to know the length of an animal track
as it moves over over the land surface. GPS measurements are accurate in the
horizontal dimensions and don't represent elevation very wel. However for nearly
any part of the earth accurate DEMs exist, so that we can combine the two sources
to recreate a 3D path.

```{r example}
require(raster)
elev <- raster(ncol=30, nrow=30,ext=extent(0,30,0,30),crs=NA)
values(elev) <- runif(ncell(elev))*10
p1 <- cbind( x=c(1,8,14,18,23), y=c(3,5,11,4,17))
p2 <- cbind( x=c(1,3,4,15,21), y=c(3,12,21,24,16))

#
p1e <- eal(p1,elev)
p2e <- eal(p2,elev)

# elevation added with resampling between observation points
p1er <- eal(p1,elev,step=1)
p2er <- eal(p2,elev,step=1)
```
## To install this package

To install this package, you should have installed the package devtools make sure that you have the package `devtools` installed (`r install.packages("devtools")`)
Next type: `r devtools::install_github("emielvanloon/amoter")`



